### 2014-03-14 paper/designspace.tex
figures for end of paper, still with placeholders but templated.  notes in identity section.

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/tubespace.png}
\caption{The design space of tubes.  Tube types, media, topologies, and design are discussed more fully in the text.  \tovi{May want star, tree added to 
your figure
}
}
\label{fig:tubespace}
\end{figure}

@@

Tube designs may emphasize either their exterior features (connection points) or their interior paths.  These two features lead to different kinds of interfaces.  An example interface that focuses on the exterior connection points is the touch sensitive toy in Figure \ref{fig:toy}, where tubes must exit the toy at the eyes, ears, tail, etc.  An interface focused on the internal path of the tube is the neon sign in Figure \ref{fig:neon}: output is based on the shape of the tube.

@@

\begin{figure*}[t]
\centering
    \includegraphics[width=\textwidth]{figures/designspace.png}
\caption{The design space of tube-based interactions.  Existing systems are written in regular font.  Those created with fabrication are in {\color{blue}blue}. In \emph{{\color{red}red italic}} are unexplored interactions creatable with custom-fabricated tubes.  Darker grey is output.  Lighter grey is input.  \valkyrie{I don't know what else might go in the blank spaces... looking for suggestions!  Also, I'm not confident this breakdown is the most clear: for example, the "liquids" category includes the copper paint, which functions as wires ("threadables"), but takes the form of a liquid...  and the general presentation of the table could probably be better in some way.  also, hello, make this wayyyyyy smaller.}}
\label{fig:designspace}
\end{figure*}

@@

Pressure can be sensed in multiple ways.  Slyper, et al., in \cite{Slyper-pressure} contribute a set of semi-closed fabricatable primitives that respond to particular actions, like twisting or pushing, with changes in internal air pressure.  \valkyrie{that sentence is not clear}  These primitives can be attached at the terminus of any semi-closed tube; the user can manipulate the printed endpoint and the system can sense air pressure changes.  Pressure can also be more simply sensed via capacitance using those techniques.

Grasp sensing can also be enabled using Wimmer's FlyEye technique \cite{Wimmer-flyeye}.  This technique involves a pair of optical links at each point of interest: one of each pair is connected to an infrared (IR) LED and the other to a camera.  When some object nears or touches a pair of cables, IR light from the LED is reflected back to the camera and the touched point appears as a bright spot.  Follmer, et al.,'s Jamming User Interfaces \cite{Follmer-jamming} rely dense particulates enclosed in a flexible volume, and can be sensed optically.  These dense particulates can be printed in-place with desired characteristics (such as varying particle size or shape) using sacrificial support material, or added post-print.  The optical links necessary for sensing with FlyEye or Jamming can be created either via clear solid cores as in \cite{Willis-printedoptics} or via fiber optic cables threaded through hollow tubes (see Figure \ref{fig:pens}).

@@

Tubes included in printed objects allow for their identification.  While the tubes need not be visible (especially in the case of fully-enclosed tubes), their presence, location, and length change the acoustic resonance properties of a printed object.

>>>>

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/tubespace.png}
\caption{The design space of tubes.  Tube types, media, topologies, and design are discussed more fully in the text.}
\label{fig:tubespace}
\end{figure}

@@

Tube designs may emphasize either their exterior features (connection points) or their interior paths.  These two features lead to different kinds of interfaces.  An example interface that focuses on the exterior connection points is the touch sensitive toy in Figure \ref{fig:toys}, where tubes must exit the toy at the eyes, ears, tail, etc.  An interface focused on the internal path of the tube is the neon sign in Figure \ref{fig:neon}: output is based on the shape of the tube.

@@

\begin{figure*}[t]
\centering
    \includegraphics[width=\textwidth]{figures/designspace.png}
\caption{The design space of tube-based interactions.  Existing systems are written in regular font.  Those created with fabrication are in {\color{blue}blue}. In \emph{{\color{red}red italic}} are unexplored interactions creatable with custom-fabricated tubes.}
\label{fig:designspace}
\end{figure*}

@@

Pressure can be sensed in multiple ways.  Slyper, et al., in \cite{Slyper-pressure} contribute a set of semi-closed 3D printable primitives that respond to particular actions, like twisting or pushing, with changes in internal air pressure.  These primitives can be attached as the terminus of any semi-closed tube; the user can manipulate the printed endpoint and the system can sense air pressure changes.  Pressure can also be more simply sensed via capacitance using those techniques.

Grasp sensing can also be enabled using Wimmer's FlyEye technique \cite{Wimmer-flyeye}.  This technique involves a pair of optical links at each point of interest: one of each pair is connected to an infrared (IR) LED and the other to a camera.  When some object nears or touches a pair of cables, IR light from the LED is reflected back to the camera and the touched point appears as a bright spot.  Follmer, et al.,'s Jamming User Interfaces \cite{Follmer-jamming} rely on dense particulates enclosed in a flexible volume, and can be sensed optically.  These dense particulates can be printed in-place with desired characteristics (such as varying particle size or shape) using sacrificial support material, or added post-print.  The optical links necessary for sensing with FlyEye or Jamming can be created either via clear solid cores as in \cite{Willis-printedoptics} or via fiber optic cables threaded through hollow tubes (see Figure \ref{fig:pens}).

@@

Tubes included in printed objects allow for their identification.  While the tubes need not be visible (especially in the case of fully-enclosed tubes), their presence, location, network structure, and length change many properties of a printed object.  This includes weight, acoustic resonance, and (if conductive material is present) capacitive signature.

\valkyrie{need to do a rewrite of this that doesn't necessarily focus so deeply on audio only.  we can talk about these other non-visible measurements like weight and capacitive signature.  I also need to actually get an intentional encoding test up and running... we are going to have to be clever about how we stimulate the resonance tubes, though.  using a speaker won't really work: we have to agitate the air in the chambers, so we might need to use something like a reed (as in reed instruments).}

### 2014-03-14 paper/exampleobjects.tex
figures for end of paper, still with placeholders but templated.  notes in identity section.

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{A touch-sensitive brain whose tubes are filled with conductive paint.  Sensing is done on a single wire via SFCS.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:toys}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{This rabbit has an open tube leading to its mouth and a semi-closed tube capped with flexible material in its back.  When air is sucked in through the open tube, the back becomes stiff as though the rabbit has breathed in.}
\label{fig:breathe}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{This radio is assembled from traditional electronic components connected by copper-filled tubes.  The case was designed to allow the components to recess into it slightly.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:radio}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{This pen holder (a) uses the FlyEye technique (b) to sense the presence or absence of an object in each of its tubes.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:pens}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{Our maze game has a large single particle trapped inside a fully enclosed tube.  It offers hours of fun!}
\label{fig:maze}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{A two-state animated neon sign designed using our tool (a)(b) \valkyrie{Tovi: we could use your PDF has to make this animate in place :)}.  (c) shows the SVG input files to create this sign, and (d) shows an isometric view of the tubes created by our tool.}
\label{fig:neon}
\end{figure}

>>>>

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/brain.png}
\caption{A touch-sensitive brain whose tubes are filled with conductive paint.  Sensing is done on a single wire via SFCS.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:toys}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/bunny.png}
\caption{This rabbit has an open tube leading to its mouth and a semi-closed tube capped with flexible material in its back.  When air is sucked in through the open tube, the back becomes stiff as though the rabbit has breathed in.  Inset shows the interior structure.}
\label{fig:breathe}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/radio.png}
\caption{This radio is assembled from traditional electronic components connected by copper-filled tubes.  The case was designed to allow the components to recess into it slightly.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:radio}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/pens.png}
\caption{This pen holder uses the FlyEye technique to sense the presence or absence of an object in each of its tubes.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:pens}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/maze.png}
\caption{Our maze game has a large single particle trapped inside a fully enclosed tube.  It offers hours of fun!}
\label{fig:maze}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/sign.png}
\caption{A two-state animated neon sign designed using our tool (a)(b) \valkyrie{Tovi: we could use your PDF hax to make this animate in place :)}.  (c) shows the SVG input files to create this sign, and (d) shows an isometric view of the tubes created by our tool.}
\label{fig:neon}
\end{figure}
